Collaborative Visual Analysis on the Web with RCloud

### 2015-06-24 casestudies.tex
fix table columns

To illustrate ...
As an example, we present a simple real-world application
deployed under RCloud.
The application is an implementation of LDAVis,
a method for visualizing large text corpora.
LDAVis helps non-experts to explore collections of
short text documents using topic modeling and
visualization. Topic modeling~\cite{Blei:2003:LDA}, although
powerful, often requires human interaction
and interpretation~\cite{Sievert:2014:LAM}.

@@

LDAVis was developed by two technical staff members at
AT\&T Labs, and originally was written in RStudio's
Shiny~\cite{RStudio:2013:SWA}, a framework for developing R
applications for the web.  While Shiny provides outstanding ease of
development, it turns out that discoverability and deployment are equally
important aspects in the lifecycle of an internal application (see
Section~\ref{sec:interviews}). In these aspects, RCloud provides a
simple solution: \emph{all developed notebooks are automatically deployed}.

@@

LDAVis highlights some unique features of RCloud.
While RCloud notebooks allow deployment of R analyses over
the web with no additional effort, RCloud \emph{applications} are more
powerful, and are developed with a combination of Javascript and HTML
for the front end. This requires additional knowledge over Shiny, but
the RCloud model makes the analysis side simpler (since analysts
simply write R in the style they already know)
and front end visualization side is simpler for the web
developers (since they simply write the Javascript code in
the style \emph{they} are used to). In addition, RCloud applications
inherit the automatic deployment and discoverability features of
all RCloud notebooks.

>>>>

LDAVis helps non-experts to explore collections of
short text documents, using topic modeling and
visualization. Topic modeling~\cite{Blei:2003:LDA},
although powerful, often requires human guidance
and interpretation~\cite{Sievert:2014:LAM}.

@@

LDAVis was developed by two technical staff members at
AT\&T Labs, originally in RStudio Shiny~\cite{RStudio:2013:SWA},
a framework for developing web applications in R.
While Shiny offers outstanding ease of development,
discoverability and deployment are also very important aspects
in an application's lifecycle (see Section~\ref{sec:interviews}).
RCloud's assumption that \emph{all developed notebooks are automatically
deployed} simplifies this for LDAVis.

@@

LDAVis highlights some unique features of RCloud.
While RCloud notebooks allow deployment of R analyses over
the web with no additional effort, RCloud \emph{applications} are more
powerful, and are developed with a combination of Javascript and HTML
for the front end. This requires additional knowledge over Shiny, but
the RCloud model makes analysis simpler (since analysts
simply write R in the style they already know)
and front end visualization side is simpler for web
developers (since they simply write the Javascript code in
the style \emph{they} know). In addition, RCloud applications
inherit the automatic deployment and discoverability features of
all RCloud notebooks.
